---
title: "Worksheet #1 Complete"
author: "Diana Lin"
date: "14/11/2019"
output: html_document
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error = FALSE, message = FALSE, warning = FALSE, fig.width=12, fig.height=8)
```

```{r setup, include=FALSE}
library(tidyverse)
library(gganimate)
library(knitr)
library(egg)
```
## Slides
Fallen behind? Here are the slides:
https://dy-lin.github.io/hs19-trends/workshop/slides_dlin.html

## Regular Bar Graph
Read in the csv file:
```{r load data, message = FALSE}
base <- "https://raw.githubusercontent.com/dy-lin/hs19-trends/master/workshop/"
seq_spec <- "data/sequencing-specific-processed.csv"
url <- paste0(base, seq_spec)
seq_data <- read_csv(url)
```

Plot the bar graph (slide 13):
```{r regular bar, out.width="600px"}
seq_data %>%
  drop_na() %>%
  ggplot(aes(x = topic, y = cum_total, fill = topic)) +
  geom_col() + 
  facet_wrap(~ Year, ncol = 8) + 
  coord_flip() +
  scale_fill_viridis_d() +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        legend.position = "bottom") +
  geom_text(aes(y = cum_total, 
                label = topic), 
            hjust = "left", 
            fontface = "bold", 
            nudge_y = 50)
```

## Racing Bar Graph
A Racing bar graph requires additional information. The ordering of the bars for each year needs to be known (slide 15):
```{r ordering racing bars}
ordered_df <- NULL

for (yr in 2003:2019) {
  order <- seq_data %>% 
    filter(Year == yr) %>% 
    arrange(cum_total) %>% 
    mutate(ordering = row_number())
  
  ordered_df <- ordered_df %>% rbind(order)
}
```

Next, let's start plotting (slide 17):
```{r racing bars animate overall}
# plot
p <- ordered_df %>% 
  ggplot(aes(ordering, group = topic)) +
  geom_col(aes(y = cum_total, width = 0.9, fill = topic)) +
  geom_text(aes(y = cum_total, label = topic), 
            hjust = "left", fontface = "bold", nudge_y = 50) +
  coord_cartesian(clip = "off", expand = FALSE) +
  scale_fill_viridis_d() +
  coord_flip() +
# animate
  transition_states(Year, transition_length = 8, state_length = 4, wrap = FALSE) +
  ease_aes("cubic-in-out") +
# aesthetics
  labs(subtitle = "Trends in sequencing methods", title = "Year {closest_state}", 
       y = "cumulative total papers") +
  theme(plot.background = element_blank(), legend.position = "none",
        axis.ticks.y = element_blank(), axis.text.y = element_blank(),
        text = element_text(size=14), plot.title = element_text(size = 35)) +
  ylim(0,1300) +
  xlab("") 
```

Now, let's animate!
```{r render animation}
# rendering the animation
animate(p, nframes = 100,
      fps = 5,
     end_pause = 10)
```

## Sankey Diagram

Let's load the packages:
```{r setup sankey, include=FALSE}
library(tidyverse)
library(ggrepel)
library(grid)
library(ggalluvial)
```

Let's read in the csv file (slide 30):
```{r read csv}
base <- "https://raw.githubusercontent.com/dy-lin/hs19-trends/master/workshop/"
SK <- "data/sankey-processed.csv"
url <- paste0(base, SK)
datSK <- read_csv(url)
```

Let's plot (slide 31):
```{r plot sankey}
sankey <- ggplot(datSK, aes(y = Weight, axis1 = From, axis2 = To)) +
  geom_alluvium(aes(fill = From), width = 1 / 12) +
  geom_stratum(alpha = 0, width = 1 / 12, color = "black") +
  scale_x_discrete(limits = c("From", "To"), expand = c(0.3, 0.1)) +
  scale_fill_viridis_d() +
  theme_void() +
  theme(axis.title.y = element_blank(), axis.title.x = element_blank(),
    axis.ticks.x = element_blank(), axis.ticks.y = element_blank(),
    axis.text.x = element_blank(),axis.text.y = element_blank(),
    legend.position = "none", plot.title = element_text(hjust = 0.5)) +
  ggrepel::geom_label_repel(
    aes(label = From), stat = "stratum", size = 3, direction = "x", hjust = 10) +
  ggrepel::geom_label_repel(
    aes(label = To), stat = "stratum", size = 3, direction = "y", nudge_x = 0.5) +
  geom_label(aes(label = Weight), stat = "stratum", alpha = 0.8) +
  ggtitle("Top 10 Institutions Publications By Topic")

sankey <- set_panel_size(sankey, width  = unit(18, "cm"), height = unit(10, "cm"))
grid.newpage()
grid.draw(sankey)
```